\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
made some funnies

We detect three large scale bright regions near
the equator of the planet, associated with persistent cloud structures
at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
likely track continents. Pronounced dark features are identified
at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
significant latitudinal extent, likely tracking oceans. Because of the
vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
high latitudes on the planet, although this may change with upcoming
sectors.

We fit Sol d with both static and time-variable albedo maps. 
\todo{We find...} 
Future observations with \TESS will yield further information on 
the time variability of surface features on Sol d.

\todo{(habitability of Sol d, speculation on landing sites)}

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Jonathan Fraine, Dan Foreman-Mackey, David W. Hogg, Ben Montet, and Ben Pope 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}

>>>>

We detect three large scale bright regions near
the equator of the planet, associated with persistent cloud structures
at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
likely track continents. Pronounced dark features are identified
at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
significant latitudinal extent, likely corresponding to oceans. Because of the
vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
high latitudes on the planet, although this may change with upcoming
sectors.

We fit Sol d with both static and time-variable albedo maps. 
We find tentative evidence for variability in Sol d's cloud coverage over 
the course of Sector 1 observations. 
Upcoming observations with \TESS will yield further information on 
the time variability of surface features on Sol d on a variety of timescales.

The likely prevalence of continents, oceans, and complex weather patterns 
on Sol d make it an extremely promising site for the evolution of life. 
We strongly advocate for future missions to further investigate this possibility. 
In particular, Sol d may be a good choice of target for a lander mission. 
One prime landing site is located at the planetary (latitude, longitude) coordinates 
($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R. Casey) led us to conclude that this would not be a suitable location.}

@@

\acknowledgements{Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
David W. Hogg, and Ben Pope for useful conversations. 
Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}
